A pipeline to analyse time-course gene expression data

### 2019-08-09 scripts/manuscript.Rmd

- I get multiple errors in compilation of file. Not sure, however, why TravisCI didn't hit these problems, so you might want to see what's going on there. Probably caching or something, so might want to occassionally remove the cache and run again, if TravisCI is saving the cache. One error I fixed, but wasn't sure about this error (changed it to `entrezgene_id` and seems to be running now...):

```
label: enrichment_analysis (with options) 
List of 2
 $ results: chr "hide"
 $ message: logi FALSE

Quitting from lines 1124-1138 (manuscript.Rmd) 
Error in getBM(attributes = c("ensembl_gene_id", "entrezgene"), filters = "refseq_mrna",  : 
  Invalid attribute(s): entrezgene 
Please use the function 'listAttributes' to get valid attribute names
Calls: <Anonymous> ... withCallingHandlers -> withVisible -> eval -> eval -> getBM
```

@@

As another sanity check, `moanin` provides a simple utility function to
visualize gene time-course data. Here, we plot the 12 genes with the smallest
p-values.

```{r fig.height=6, fig.width=6}
top_DE_genes_pval = names(sort(pvalue)[1:12])
plot_genes(data[top_DE_genes_pval, ], splines_model,
    colors=ann_colors$Group, smooth=TRUE,
    mar=c(1.5,2.5,2,0.1),legendArgs=list(title="Treatment"),
    mfrow=c(3,5))
```

@@

```{r fig.height=6, fig.width=6}
top_DE_genes_lfc = names(
    sort(abs(lfc_epicon),
	 decreasing=TRUE)[1:12])
plot_genes(data[top_DE_genes_lfc, ], splines_model,
		   colors=ann_colors$Group, smooth=TRUE)

>>>>

@@

As another sanity check, `moanin` provides a simple utility function to
visualize gene time-course data. Here, we plot the 10 genes with the smallest
p-values.

```{r fig.height=6, fig.width=6}
top_DE_genes_pval = names(sort(pvalue)[1:10])
plot_genes(data[top_DE_genes_pval, ], splines_model,
    colors=ann_colors$Group, smooth=TRUE,
    mar=c(1.5,2.5,2,0.1), legendArgs=list(title="Treatment"))
```

@@

```{r fig.height=6, fig.width=6}
top_DE_genes_lfc = names(
    sort(abs(lfc_epicon),
	 decreasing=TRUE)[1:10])
plot_genes(data[top_DE_genes_lfc, ], splines_model,
    colors=ann_colors$Group, smooth=TRUE,
    mar=c(1.5,2.5,2,0.1), legendArgs=list(title="Treatment"))
